PANCHANGE_analysis

### 2020-12-18 PANCHANGE_analysis.Rmd
fixed age reference cat in employment regression

```{r model1b employment prior covid function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

### add a single "other ethnicity individual" as a jitter for NBR so this category remains included wihout adding explanation.
```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}
dat.retro.nbr$Ethnicity_collapsed[586] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[856] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[871] <- "Other"  #this person was an NA

@@

pcl.retro.lm.glad <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                            dat.retro.glad)
pcl.retro.lm.nbr <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                            dat.retro.nbr)
pcl.retro.lm.ramp <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                            dat.retro.ramp)

@@

lmoutput_format(pcl.retro.lm.glad,"PCL.retrospective","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
lmoutput_format(pcl.retro.lm.nbr,"PCL.retrospective","NBR", "pcl.retro.lm.for.plot.NBR")
lmoutput_format(pcl.retro.lm.ramp,"PCL.retrospective","RAMP", "pcl.retro.lm.for.plot.RAMP")

@@

plot.dat.sample.pcl <- rbind(pcl.retro.lm.for.plot.GLAD,
                             pcl.retro.lm.for.plot.NBR,
                             pcl.retro.lm.for.plot.RAMP)

@@

```{r forest plot by sample retro only pcl, fig.height=30, fig.width=50, dpi=120}

lm.forest(plot.dat.sample.pcl ,"Predictors of PTSD controlling for retrospective symptoms across samples")

>>>>

```{r model1b employment prior covid function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

### add a single "other ethnicity individual" as a jitter for NBR so this category remains included wihout adding explanation.
```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}

dat.retro.nbr$Ethnicity_collapsed[586] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[856] <- "Other"  #this person was an NA
dat.retro.nbr$Ethnicity_collapsed[989] <- "Other"  #this person was an NA

@@

@@

@@

@@
